Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Section~\ref{} style.

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
    (Section \ref{sec:haddock} and \ref{sec:doctest})
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

\item
    We introduce a set of combinators to express expectations about
    code examples for use with Hspec (Section \ref{sec:code-doc} and
    Section \ref{sec:hspec-comb})

\item
    We improve CI support for Doctest and Hspec (Section
    \ref{sec:TBD})

@@

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section \ref{ref:Best-current-practice})

@@

As we explained in Section \ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two extensions to Haddock's markup.
And combinators for expectations, that can be used with Hspec, are
introduced.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
\label{sec:solution-discovery}
We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
\ref{sec:problem-discovery}.

@@

\noindent All combinators introduced in \ref{sec:code-doc} have been
implemented.  They are available form Hackage\footnote{%
http://hackage.haskell.org/package/hspec-shouldbe},
and they will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.

@@

As discussed in \ref{sec:solution-discovery}, we use a preprocessor to
automatically generate test drivers for Hspec.  GHC invokes the
preprocessor with three arguments:

@@

As discussed in \ref{sec:solution-discovery}, we can use {\tt
hspec-discover} to automatically generate a test driver for Hspec:

>>>>

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
    (Section~\ref{sec:haddock} and Section~\ref{sec:doctest})
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section~\ref{sec:user-doc} and Section~\ref{sec:doctest})

\item
    We introduce a set of combinators to express expectations about
    code examples for use with Hspec
    (Section~\ref{sec:code-doc} and Section~\ref{sec:hspec-comb})

\item
    We improve CI support for Doctest and Hspec
    (Section~\ref{sec:TBD})

@@

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section~\ref{ref:Best-current-practice})

@@

As we explained in Section~\ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two extensions to Haddock's markup.
And combinators for expectations, that can be used with Hspec, are
introduced.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
\label{sec:solution-discovery}
We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
Section~\ref{sec:problem-discovery}.

@@

\noindent All combinators introduced in Section~\ref{sec:code-doc} have been
implemented.  They are available form Hackage\footnote{%
http://hackage.haskell.org/package/hspec-shouldbe},
and they will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.

@@

As discussed in Section~\ref{sec:solution-discovery}, we use a preprocessor to
automatically generate test drivers for Hspec.  GHC invokes the
preprocessor with three arguments:

@@

As discussed in Section~\ref{sec:solution-discovery}, we can use
{\tt hspec-discover} to automatically generate a test driver for Hspec:
